---
name: Thomas 
surname: Spoehr
position: "Statistics Graduate Student"
pronouns: him/his
address: "14782 Eagle St., Bennington, NE"
phone: 402-671-4622
www: www.linkedin.com/in/thomas-spoehr-5030b22a8
email: "spoehrt1@gmail.com"
#twitter: mariecurie
github: tspoehr33
#linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
```

# Professional Summary
Current PhD statistics student with past internship experience and a passion for analyzing/synthesizing data for informed, logical decision-making. Skilled in technical programs such as Python, R, and Microsoft Excel which allow for streamlined results and efficient analysis.

```{r}
# library(readxl)
# filename <- read_excel("CV_data.xlsx")
```


# Education

```{r} 
library(tibble)
tribble(
  ~ Degree, ~ Years, ~ Institution, ~ Where,
  "Mathematics", "2018 - 2022", "Central College", "Pella, IA",
  "Masters of Arts - Mathematics", "2022 - 2025", "University of Nebraska - Omaha", "Omaha, NE",
  "Doctorate of Statistics", "2025 - Current", "University of Nebraska - Lincoln", "Lincoln, NE"
) %>%
  detailed_entries(Degree, Years, Institution, Where)
```

# Teaching and Advising 

```{r}
library(tibble)
tribble(
  ~ what, ~ when, ~ with, ~ where, ~ why,
  "Teaching Assistant", "2025 - Current", "Department of Statistics", "University of Nebraska-Lincoln", list("Planned lessons and assignments, conducted office hours, graded papers and exams", "Acted as teaching assistant for a section of introductory statistics", "Composed and assessed all exams"),
  "Teaching Assistant", "2023 - 2025", "Department of Mathematics", "University of Nebraska-Omaha", list("Acted as an instructor of record for multiple sections of college algebra", "Implemented active learning techniques with a student focused paradigm", "Applied a standards-based grading system to further student learning and success"),
  "Teaching Assistant", "2022 - 2023", "Department of Mathematics", "University of Minnesota State - Mankato", list("Acted as instructor of record for multiple sections of precalculus", "Created all materials for course including exams, assignments, and presentation slides", "Graded all assessments for the course")
) %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
    )
```


# Research

```{r}
library(tibble)
tribble(
  ~ what, ~ when, ~ with, ~ why,
  "Master's Student Research", "2024-2025", "University of Nebraska – Omaha",
  list("Conducted original research which expanded upon existing works in image cryptography", "Created a novel chaotic map and new encryption methodology for more effective and efficient image cryptography", "Failed submission to “Signal Image Processing”; currently resubmitting to other peer-reviewed journals")
) %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why
    )
```


# Conference Presentations

```{r}
library(tibble)
tribble(
  ~ what, ~ when, ~where, ~ why,
  "Exploring the relationship between preexisting attitudes and resulting attitudes in a first-year college algebra course", "Spring 2025", "Alexandria, VA", "Research for Undergraduate Math Education",
  "An Innovative Encryption Algorithm Employing Multistep Pixel Manipulation via an Enhanced Chaotic System", "Spring 2025", "Omaha, NE", "MAA Sectional Meeting",
  "Exploring the relationship between preexisting attitudes and resulting attitudes in a first year college algebra course", "Spring 2024", "Vermillion, SD", "MAA Sectional Meeting",
  "Midwest Sports Analytics Conference Co-Director", "Fall 2020, 2021", "Pella, IA", "Co-Director",
  "Investigating the relation between acceleration and impacts on goalies in soccer", "Fall 2020", "Pella, IA", "Midwest Sports Analyics Conference")  %>%
  detailed_entries(
    what = what,
    when = when,
    where = where,
    why = why
    )
  
```


#Honors and Awards
```{r}
library(tibble)
 tribble(
   ~ what, ~ when, ~ with, ~ why,
   "Othmer Fellowship", "2025-Present", "University of Nebraska - Lincoln", "For perceived excelence in candiancy for PhD studies",
   "APC Meeting Speaker", "2025", "University of Nebraska - Lincoln", "Selected as lone graduate student speaker to defend departmental cuts",
   "Academic Scholarship", "2018-2022", "Central College", "For excellent academic standing") %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    why = why
    )

```


# Other 
```{r}
library(tibble)
 tribble(
   ~ what, ~ when, ~ with,
   "Member of Graduate Student Association", "2025", "University of Nebraska-Lincoln",
   "Member of Graphics Group", "2025", "University of Nebraska-Lincoln",
   "Volunteer at UNO High School Math Competition", "2024", "University of Nebraska-Omaha") %>%
  detailed_entries(
    what = what,
    when = when,
    with = with
    )
```

# Industry
```{r}
library(tibble)
 tribble(
   ~ what, ~ when, ~ with, ~ where, ~ why,
   "Supply Chain and Logistics Data Intern", "Summer 2025", "Smeal Fire Appartus", "Snyder. NE", list("Created an automated process using
Python to monitor vendor quality", "Utilized Microsoft Excel to perform
extensive analysis on daily, excess, and obsolete inventory which cut 15% of
unnecessary stock")) %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
    )
```


# References

```{r}
library(tibble)
 tribble(
    ~ what, ~ when, ~ with, ~ where, ~ why,
   "Dora Velcsov", "Professor of Mathematics", "University of Nebraska - Omaha",
   "402-554-3295", "dvelcsov@unomaha.edu", 
   "Russell Goodman", "Professor of Mathematics", "Central College",
  "641-628-7640", "goodmanr@central.edu")%>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
    )
```   
   


